Bow shocks, bow waves, and dust waves

### 2019-01-21 papers/Papers1234/app-dust-equations.tex
Draine & Salpeter equations in Appendix C

>>>>

Following \citet{Draine:1979a}, the drag force on a grain that is
moving at relative velocity \(w\) through a partially ionized gas can
be written as a sum over each collider species, \(k\), with mass
\(m_k\), abundance relative to hydrogen \(\alpha_k\) and charge
\(z_k\). If the velocity is normalized to the thermal velocity of each
species:
\begin{equation}
  \label{eq:s-velocity}
  s_k = \left( m_k w^2 / 2 k T  \right)^{1/2} \ ,
\end{equation}
then the force is given by
\begin{equation}
  \label{eq:ds79}
  f\drag = f_* \sum_k \alpha_k \left[ G_0(s_k) + z_k^2 \phi^2 \ln(\Lambda/z_k) G_2(s_k) \right],
\end{equation}
where \(f_*\) is a characteristic thermal force on the grain
(see eq.~[\ref{eq:fstar}]). The
dimensionless functions of normalized speed \(G_0(s)\) and \(G_2(s)\)
are given by
\begin{align}
  \label{eq:G0}
  G_0(s) & = \left( s^2 + 1 - \frac{1}{4 s^2} \right) \erf(s)
  +  \left( s + \frac{1}{2 s} \right) \frac{e^{-s^2}}{\sqrt{\pi}}\\
  \label{eq:G2}
  G_2(s) & = \frac{\erf(s)}{s^2} - \frac{2 e^{-s^2}}{s \sqrt{\pi}} \ .
\end{align}
The \(G_0\) term is due to inelastic solid-body collisions in the
Epstein limit, and is derived in \S~4 of \citet{Baines:1965a}.  The
\(G_2\) term is due to electrostatic Coulomb interactions, with
\(\phi\) being the grain potential in thermal units
(eq.~[\ref{eq:phi-potential}]) and \(\Lambda\) the plasma parameter.  It was
first derived in the different context of dynamic friction in stellar
systems by \citet{Chandrasekhar:1941a}.

We provide a python implementation of these equations in the file
\texttt{ds79.py}, available from
\url{https://github.com/div-B-equals-0/dust-trajectories}.
Figure~\ref{fig:drag-components}--\ref{fig:gas-grain-drag-photoionized}
show example applications to gas--grain drag in a photoionized region.
